Type cones of $\b{g}$-vector fans

### 2019-02-15 thirdPaper/draft/typeConeAssociahedra.tex
Very minor corrections.
modified setting for extricat: removed KS

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Relations for~$\b{g}$-vectors in brick algebras via extriangulated categories}

%%%%
\subsection{Setting}\label{setting::extricat}

In this section, we let~$\cat$ be a Krull--Schmidt, extriangulated category with a fixed full additive \yann{additive contains strictly full + stable under taking summands} subcategory~$\tc$ satisfying the following three properties:
\begin{enumerate}
 \item Every~$T\in\tc$ is projective in~$\cat$;
 \item For each~$T\in\tc$, the morphism~$T\to 0$ is an inflation for the extriangulated structure of~$\cat$;
 \item For each~$X\in\cat$, there is an extriangle~$T_1^X\infl T_0^X \defl X \overset{\delta_X}{\dashrightarrow}$ in~$\cat$ with~$T_0^X, T_1^X$ in~$\tc$.
\end{enumerate}

@@

\yann{Rappels sur les categories extriangulees}
%%%%
\subsection{Statement of preliminary results on extriangulated categories}
\label{subsection: prelim on extricats}

@@

\subsection{Statement of the theorem}

@@

%%%%
\subsection{Proof of Theorem~\ref{theorem::extricats}}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Relations for~$\b{g}$-vectors in brick algebras via extriangulated categories}
\label{sect::extricats}
%%%%
\subsection{Setting}\label{setting::extricat}

\noindent {\bf Setting for Section~\ref{sect::prelim on extricats}}
In that section, we let~$\cat$ be an extriangulated category with a fixed full additive \yann{additive contains strictly full + stable under taking summands} subcategory~$\tc$ satisfying the following three properties:
\begin{enumerate}
 \item Every~$T\in\tc$ is projective in~$\cat$;
 \item For each~$T\in\tc$, the morphism~$T\to 0$ is an inflation for the extriangulated structure of~$\cat$;
 \item For each~$X\in\cat$, there is an extriangle~$T_1^X\infl T_0^X \defl X \overset{\delta_X}{\dashrightarrow}$ in~$\cat$ with~$T_0^X, T_1^X$ in~$\tc$.
\end{enumerate}

\noindent {\bf Setting for Section~\ref{sect::Statment extricats}}
We that section, we keep the previous setting, but assume moreover that~$\cat$ is Krull--Schmidt, Ext-finite, and has Auslander--Reiten--Serre duality.

@@

\yann{Rappels sur les categories extriangulees}
%%%%
\subsection{Statement of preliminary results on extriangulated categories}
\label{sect::prelim on extricats}

So as to be able to state the main theorem of Section~\ref{sect::extricats}, we need a few results on extriangulated categories.
However, all proofs are postpone to Section~\ref{sect::proofs extricats}.

@@

\subsection{Statement of the theorem}
\label{sect::Statment extricats}

@@

%%%%
\subsection{Proof of Theorem~\ref{theorem::extricats}}
\label{sect::proofs extricats}
